---
title: "Run Model & Generate Plots"
author: "Cindy Chen, cjc2279"
date: '2022-11-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstanarm)
library(ggplot2)
library(brms)
library(bayesplot)
options(mc.cores = parallel::detectCores())
```

## Test out different priors

```{r bail}
brm_test <- brm(bail_amt ~ general_age + Race + Gender + Ethnicity + mo(Top_Charge_Arraign_Ordinal) + estimated_income + Representation_PubPriv + prior_vfo_cnt + prior_nonvfo_cnt + prior_misd_cnt + after_july_2020 + after_july_2020:Race +
      (1 + Race + Ethnicity + after_july_2020 + after_july_2020:Race | Judge_Name),
    data = merged_data,
    family = gaussian,
    prior = c(prior(normal(log(20000), log(10000)), class = 'Intercept'),
              prior(normal(log(5000), log(3000)), class = 'b')),
    seed = 12042022,
    control = list(adapt_delta = 0.93),
    chains = 4,
    iter = 10000
    )

```


### Generate all judge-specific coefficients and save them in a separate file
```{r}
judge_coef <- coef(brm_test)
write.csv(judge_coef, "judge_coef.csv")
```

### Plot conditional effects of Estimated Income and Race
```{r}
plot(conditional_effects(brm_test, effects = "estimated_income:Race"))
```

### Plot conditional effects of Estimated Income and Charge Severity
```{r}
# can only do this with ordinal variables... not for continuous!
plot(conditional_effects(brm_test, effects = "estimated_income:Top_Charge_Arraign_Ordinal"))
```

### Generate all summary statistics
```{r}
summary(brm_test)
```

### Plot conditional effects of Charge Severity and Race
```{r}
plot(conditional_effects(brm_test, effects = "Top_Charge_Arraign_Ordinal:Race"))
```

### Plot all coefficients, standard deviations, and correlations
```{r}
plot(brm_test)
```

### Plot conditional effects of Age and Race
```{r}
plot(conditional_effects(brm_test, effects = "general_age:Race"))
```

### Plot conditional effects of July 2020 and Race
```{r}
plot(conditional_effects(brm_test, effects = "after_july_2020:Race"))
```

### Plot conditional effects of Prior Violent Felony Count
```{r}
plot(conditional_effects(brm_test, effects = "prior_vfo_cnt"))
```

### Plot conditional effects of Charge Severity
```{r}
plot(conditional_effects(brm_test, effects = "Top_Charge_Arraign_Ordinal"))
```

### Plot conditional effects of Race and Ethnicity
```{r}
plot(conditional_effects(brm_test, effects = "Race:Ethnicity"))
```

### Plot conditional effects of Ethnicity and July 2020
```{r}
plot(conditional_effects(brm_test, effects = "after_july_2020:Ethnicity"))
```

### Plot the 'leave-one-out'
```{r}
plot(loo(brm_test, k_threshold = 0.7), label_points = TRUE)
```

### Plot conditional effects of Charge Severity and Race
```{r}
plot(conditional_effects(brm_test, effects = "Top_Charge_Arraign_Ordinal:Race"))
```